An open source scientific article

### 2021-10-18 src/ms.tex
slow n steady

% Author list
\author{First Author}

@@

% Main body
\section{Introduction}

Figure~\ref{fig:fibonacci} is an example of a figure that depends on an external dataset.
In order to tell \texttt{showyourwork} about this extra dependency (and how to download it), a custom rule must be added to the \texttt{Snakefile}.

% A sample figure generated from an external dataset
\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=0.75\linewidth]{figures/fibonacci.pdf}
        \caption{
            A sample figure showing the Fibonacci sequence in binary.
            This figure was generated from a dataset hosted externally on Zenodo. 
            The instructions for downloading this dataset and making it an explicit dependency of this figure are specified in the \texttt{Snakefile}.
        }
        % This label tells showyourwork that the script `figures/fibonacci.py'
        % generates the PDF included above
        \label{fig:fibonacci}
    \end{centering}
\end{figure}

>>>>

% Author list
\author{Adina~D.~Feinstein}

@@

% Main body with filler text
\section{Introduction}
\Blindtext[4]
